Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
consistent Schema.org capitalisation

To further verify this idea of simplicity, we have formalised the
RO-Crate definition (see \textit{Appendix~\ref{sec:formaldefinition})}). An
important result of this exercise is that the underlying data structure
of RO-Crate, although conceptually a graph, is represented as a
depth-limited tree. This formalisation also emphasises the
\textit{boundedness} of the structure; namely, the fact that elements are
specifically identified as being either semantically \textit{contained} by the
RO-Crate as \textit{Data Entities} (\texttt{hasPart}) or mainly referenced
(\texttt{mentions}) and typed as \textit{external} to the Research Object as
\textit{Contextual Entities}. It is worth pointing out that this semantic
containment can extend beyond the physical containment of files
residing within the RO-Crate Root directory on a given storage system,
as the RO-Crate data entities may include any data resource globally
identifiable using IRIs.
\subsubsection{Extensibility and RO-Crate profiles}% {#profiles}

@@

The main addition in the upcoming 1.2 release of the RO-Crate
specifications will be the formalization of
profiles\footnote{\url{https://www.researchobject.org/ro-crate/1.2-DRAFT/profiles}}
for different categories of crates. Additional entity types have been
requested by users, e.g. workflow runs, business workflows, containers
and software packages, tabular data structures; these are not always
matched well with existing Schema.org types but may benefit from other
vocabularies or even separate metadata files, e.g. from Frictionless
Data.\footnote{\url{https://frictionlessdata.io/}} We will be further aligning with
and collaborating with related research artefact description efforts
like CodeMeta\footnote{\url{https://codemeta.github.io/}} for software metadata,
Science-on-schema.org\footnote{\url{https://science-on-schema.org/}}
\cite{doi:10.5281/zenodo.4477164} for datasets, FAIR Digital
Objects\footnote{\url{https://fairdo.org/}} \cite{doi:10.3390/publications8020021} and
activities in EOSC task forces\footnote{\url{https://www.eosc.eu/task-force-faq}}
including the EOSC Interoperability Framework \cite{doi:10.2777/620649}.

@@

\subsection{Mapping to RDF with schema.org}

>>>>

To further verify this idea of simplicity, we have formalised the
RO-Crate definition (see \textit{Appendix~\ref{sec:formaldefinition}}). An
important result of this exercise is that the underlying data structure
of RO-Crate, although conceptually a graph, is represented as a
depth-limited tree. This formalisation also emphasises the
\textit{boundedness} of the structure; namely, the fact that elements are
specifically identified as being either semantically \textit{contained} by the
RO-Crate as \textit{Data Entities} (\texttt{hasPart}) or mainly referenced
(\texttt{mentions}) and typed as \textit{external} to the Research Object as
\textit{Contextual Entities}. It is worth pointing out that this semantic
containment can extend beyond the physical containment of files
residing within the RO-Crate Root directory on a given storage system,
as the RO-Crate data entities may include any data resource globally
identifiable using IRIs.
\subsubsection{Extensibility and RO-Crate profiles}% {#profiles}

@@

The main addition in the upcoming 1.2 release of the RO-Crate
specifications will be the formalization of
profiles\footnote{\url{https://www.researchobject.org/ro-crate/1.2-DRAFT/profiles}}
for different categories of crates. Additional entity types have been
requested by users, e.g. workflow runs, business workflows, containers
and software packages, tabular data structures; these are not always
matched well with existing Schema.org types but may benefit from other
vocabularies or even separate metadata files, e.g. from Frictionless
Data.\footnote{\url{https://frictionlessdata.io/}} We will be further aligning with
and collaborating with related research artefact description efforts
like CodeMeta\footnote{\url{https://codemeta.github.io/}} for software metadata,
Science-on-Schema.org\footnote{\url{https://science-on-schema.org/}}
\cite{doi:10.5281/zenodo.4477164} for datasets, FAIR Digital
Objects\footnote{\url{https://fairdo.org/}} \cite{doi:10.3390/publications8020021} and
activities in EOSC task forces\footnote{\url{https://www.eosc.eu/task-force-faq}}
including the EOSC Interoperability Framework \cite{doi:10.2777/620649}.

@@

\subsection{Mapping to RDF with Schema.org}
